Secure Multi-Party Computation with SCALE-MAMBA

### 2019-03-11 paper.tex
Added online phase/ only thing missing is the improvemetn with different beaver triples.

\subsubsection{Oblivious Transfer}

@@

TODO: SOUNDNESS SLACK
TODO: LATTICE BASED CRYPTOGRAPHY

Scale-Mamba is an implementation of SPDZ among other protocols. SPDZ is right now the most efficient protocol in use.

Most LSSS-based MPC protocols split the computation into two parts: an of-

ine phase, in which parties interact using expensive" public-key cryptography
to lay the groundwork for an online phase in which only cheap" informationtheoretic
primitives are required. The online phase is where the actual circuit
evaluation takes place. For the access structures considered in this work, namely
Q2 structures, the offline phase is almost as fast as the online phase. Thus the
goal here is to minimize the cost of communication in both phases.

@@

In general, the SMPC protocol is split in two parts, first an offline phase and secondly and online phase. In the online phase only the final evaluation of the function is executed. In the offline phase, prior to the online phase, preparations are done by all the parties to prepare for the evaluation. This includes already calculating values for possible multiplications and MACs, so that the online phase can be executed faster. This phase is not completly offline, because the parties still exchange some information which are later needed for the evaluation. But this phasae is not that time critically, that means it can be already executed a lot earlier than the online phase, so that, when the function evaluation is really needed, the result can be calculated in a rather fast time compared to a system that still has to set up everything. In SCALE-MAMBA, compared to its predecessors, the offline and online phase are completly integrated. Therefore, it is not possible anymore to execute them separately like in SPDZ for example. But it is a much closer approach to a real world application.\\

@@

Now we assume that the offline phase was succesfully executed, so all preliminaries are given to execute the online phase. It's main goal is to evaluate a specified circuit with secret inputs by the different parties. So this is the heart of the system, the part where the real computatiuon is executed. 
It is important to note, that the online phase is nearly perfectly optimized when assuming the offline phase was carried out succesfully. The online phase has a runtime complexity in O(n), and therefore there is not a really big performance impact. It is also noteworthy, that in the online phase only only computational and no information theoretical problems are solved. All this leads to the fact, that there is not really any change in the online phase in the SPDZ like protocols in the last years, therefore the online phase is the same like in the earlier version of SPDZ ~\cite{cryptoeprint:2011:535}.\\

@@

\subsubsection{Multiplication with constant}
Multiplicating with a public constant is as well really simple and can also be done by each party invdividually. It is defined as:\\
$$c*\langle a\rangle=\langle c*a\rangle=(c*\delta,(c*a_1,...,c*a_n),,(c*\gamma (a)_1,...,c*\gamma (a)_n)$$
\textbf{Correctness}:(TO BE DONE\\

>>>>

\subsubsection{Oblivious Transfer}
While Oblivious Transfer (OT) is not of direct importance for this thesis, the general concept should still be known to the reader.

@@

@@

In general, the SMPC protocol is split in two parts, first an offline phase and secondly and online phase. In the online phase only the final evaluation of the function is executed. In the offline phase, prior to the online phase, preparations are done by all the parties to prepare for the evaluation. This includes already calculating values for possible multiplications and MACs, so that the online phase can be executed faster. In this phase the expensive calculations are done, like public key cryptography or authentifications, so that the online phase only needs basic primitives. This phase is not completly offline, because the parties still exchange some information which are later needed for the evaluation. But this phasae is not that time critically, that means it can be already executed a lot earlier than the online phase, so that, when the function evaluation is really needed, the result can be calculated in a rather fast time compared to a system that still has to set up everything. In SCALE-MAMBA, compared to its predecessors, the offline and online phase are completly integrated. Therefore, it is not possible anymore to execute them separately like in SPDZ for example. But it is a much closer approach to a real world application.\\

@@

Now we assume that the offline phase was succesfully executed, so all preliminaries are given to execute the online phase. It's main goal is to evaluate a specified circuit with secret inputs by the different parties. So this is the heart of the system, the part where the real computatiuon is executed. \\
It is important to note, that the online phase is nearly perfectly optimized when assuming the offline phase was carried out succesfully. The online phase has a runtime complexity in O(n), and therefore there is not a really big performance impact. It is also noteworthy, that in the online phase only only computational and no information theoretical problems are solved. All this leads to the fact, that there is not really any change in the online phase in the SPDZ like protocols in the last years, therefore the online phase is the same like in the earlier version of SPDZ ~\cite{cryptoeprint:2011:535}.\\

@@

\subsubsection{Multiplication with constant}
Multiplicating with a public constant is as well really simple and can also be done by each party invdividually. It is defined as:\\
$$c*\langle a\rangle=\langle c*a\rangle=(c*\delta,(c*a_1,...,c*a_n),,(c*\gamma (a)_1,...,c*\gamma (a)_n)$$
\textbf{Correctness}: We have to examine the different parts, to see each parts correctness: \\

\begin{enumerate}
\item \(  c*a = c * (a_1+....+a_n) = c*a_1+...+c*a_n \)
\item \( \gamma (c*a) = \alpha*(c*a) = c*(\alpha * a) = c * \gamma (a) = c* ( \gamma (a)_1+...+\gamma (a)_n)  \)
\end{enumerate}
